Constraining the Interiors of Asteroids Through Close Encounters

### 2022-06-30 paper/main.tex
Hessian spread on mcmc points

Specifically, we highlight both the uncertainties on the density moments and uncertainty on density distribution. Moment uncertainty is defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD for each $\ell$ and $m$. Since there is no degeneracy between moments and the actual encounter data, this uncertainty is well-defined. However, its physical relevance is not obvious. The density distribution uncertainty is presented as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each made using a different sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}. The average uncertainty over this map, divided by the local density, is taken as the uncertainty in density distribution of the asteroid. This measure of uncertainty is more physically relevant than moment uncertainty, but it is affected by choices of the density distribution model, degrees of freedom, prior constraints, and other effects unrelated to the encounter properties.

@@

\begin{table}
  \centering
  \begin{tabular}{lll} \hline
    Encounter property & $\sigma_\rho / \rho = 100\%$ & $20\%$ \\ \hline
    Perigee ($r_p$, Earth radii) & $<$7.9 & $<$4.7 \\
    Excess velocity ($v_\infty$) & - & - \\
    Asteroid length ($a_\mathcal{A}$, m) & $>$180 & $>$1100 \\
    Period ($P_\omega$, hr) & $>$4.3 & $>$9.5\\ \hline
    Spin period uncertainty ($P_\omega \sigma_\rho$, ms) & $<$15 & $<$3.1\\
    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$2.8 & $<$0.5 \\
    Cadence ($\Delta t$, min) & $<$38 & $<$2 \\
    Data gap ($T_\text{gap}$, hr) & $<$1.8 & $<$0 \\ 
    \hline
  \end{tabular}
  \caption{The physical / observational encounter property thresholds (\textit{top} / \textit{bottom} consistent with useable density distribution uncertainty. \jtd{Summarizing sentence}.}
  \label{tab:threshold-summary}
\end{table}

In table \ref{tab:threshold-summary}, we present the property ``thresholds'' required in order to obtain meaningful information about the asteroid density distribution. These are collected by \jtd{Explain}. Their values are also shown in figures \ref{fig:scan-physical} to \ref{fig:scan-observational} as vertical red lines. These thresholds are more physically relevant, but they should be understood as moveable, since making different model choices can drastically change their locations.

\begin{figure*}
  \newpage
  \centering
  \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all1.pdf}
  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty. The vertical dashed line indicates the reference asteroid values. The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
  \label{fig:scan-perigee}
  \label{fig:scan-vex}
  \label{fig:scan-am}
  \label{fig:scan-period}
  \label{fig:scan-physical}
\end{figure*}

\begin{figure*}
  \newpage
  \centering
  \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all2.pdf}
  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period. The vertical dashed line indicates the reference asteroid values. The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
    \label{fig:scan-rho}
    \label{fig:scan-theta}
    \label{fig:scan-cadence}
    \label{fig:observation-gap}
    \label{fig:scan-observational}
\end{figure*}

@@

>>>>

Specifically, we highlight both the uncertainties on the density moments and uncertainty on density distribution. Moment uncertainty is defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD for each $\ell$ and $m$. Since there is no degeneracy between moments and the actual encounter data, this uncertainty is well-defined. However, its physical relevance is not obvious. The density distribution uncertainty is presented as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each made using a different sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}. The median uncertainty over this map, divided by the local density, is taken as the uncertainty in density distribution of the asteroid. This measure of uncertainty is more physically relevant than moment uncertainty, but it is affected by choices of the density distribution model, degrees of freedom, prior constraints, and other effects unrelated to the encounter properties.

\begin{table}
  \centering
  \begin{tabular}{lll} \hline
    Encounter property & Weak &Strong \\ \hline
    Perigee ($r_p$, Earth radii) & $<$6.0 & $<$18\\
    Excess velocity ($v_\infty$) & - & - \\
    Asteroid length ($a_\mathcal{A}$, m) & $>$15 & - \\
    Period ($P_\omega$, hr) & $>$7.6 & - \\ \hline
    Spin period uncertainty ($\sigma_P$, ms) & $<$12 & $<$270\\
    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$1.9 & $<$35 \\
    Cadence ($\Delta t$, min) & $<$15 & - \\
    Data gap ($T_\text{gap}$, hr) & - & - \\ 
    \hline
  \end{tabular}
  \caption{The weak and strong thresholds on physical / observational properties (\textit{top} / \textit{bottom}) consistent with useable density distribution uncertainty. Perigee and observational uncertainty are the most constraining properties, followed by asteroid length, rotational period, and observational cadence.}
  \label{tab:threshold-summary}
\end{table}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/unc-scan.pdf}
  \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution as a function of various encounter properties. Density distributions from both the lumpy and finite element models are used. The benchmark uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded. The figures illustrate the marked difference in density distributions that results from using different models.}
  \label{fig:net-uncertainty}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all1.pdf}
  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty. The vertical dashed line indicates the reference asteroid values. The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
  \label{fig:scan-perigee}
  \label{fig:scan-vex}
  \label{fig:scan-am}
  \label{fig:scan-period}
  \label{fig:scan-physical}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all2.pdf}
  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period. The vertical dashed line indicates the reference asteroid values. The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
    \label{fig:scan-rho}
    \label{fig:scan-theta}
    \label{fig:scan-cadence}
    \label{fig:observation-gap}
    \label{fig:scan-observational}
\end{figure*}

@@

In table \ref{tab:threshold-summary}, we present the property ``thresholds'' required in order to obtain meaningful information about the asteroid density distribution. These are collected by evaluating the median uncertainty ratio of the asteroid density distribution extracted by the lumpy model as a function of each encounter property and identifying when it exceeds $\sigma_\rho / \rho = 10^{-4}$ (the weak threshold) and $\sigma_\rho / \rho = 10^{-3}$ (the strong threshold). These thresholds are also shown in figures \ref{fig:scan-physical} to \ref{fig:scan-observational} as vertical red lines. The values of $\sigma_\rho / \rho$ are plotted as a function of encounter properties in figure \ref{fig:net-uncertainty}, similarly to figures \ref{fig:scan-physical} and \ref{fig:scan-observational}.
